The \dealii Library, Version 9.6

### 2024-08-16 9.6/paper.tex
Update affiliation

\newcommand{\specialword}[1]{\texttt{#1}}
\newcommand{\dealii}{{\specialword{deal.II}}\xspace}
\newcommand{\pfrst}{{\specialword{p4est}}\xspace}
\newcommand{\trilinos}{{\specialword{Trilinos}}\xspace}
\newcommand{\epetra}{{\specialword{Epetra}}\xspace}
\newcommand{\tpetra}{{\specialword{Tpetra}}\xspace}
\newcommand{\aspect}{\specialword{Aspect}\xspace}
\newcommand{\petsc}{\specialword{PETSc}\xspace}
\newcommand{\snes}{{\specialword{SNES}}\xspace}
\newcommand{\ts}{{\specialword{TS}}\xspace}
\newcommand{\petscsf}{{\specialword{SF}}\xspace}
\newcommand{\cmake}{{\specialword{CMake}}\xspace}
\newcommand{\candi}{{\specialword{candi}}\xspace}
\newcommand{\sundials}{{\specialword{SUNDIALS}}\xspace}
\newcommand{\kinsol}{{\specialword{KINSOL}}\xspace}
\newcommand{\ida}{{\specialword{IDA}}\xspace}
\newcommand{\arkode}{{\specialword{ARKODE}}\xspace}
\newcommand{\boost}{{\specialword{Boost}}\xspace}
\newcommand{\kokkos}{{\specialword{Kokkos}}\xspace}

@@

\author[8]{Timo~Heister}
 \affil[8]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

\author[9]{Luca~Heltai}
\affil[9]{University of Pisa, Italy}

 \author[10]{Martin~Kronbichler}
 \affil[10]{Ruhr University Bochum, Germany}

\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[12]{Peter Munch}
 \affil[12]{Uppsala University, Sweden.
  {\texttt{peter.munch@it.uu.se}}}

\author[13]{Magdalena Schreter-Fleischhacker}
 \affil[13]{Institute for Computational Mechanics, Technical University of Munich, Boltzmannstraße 15, 85748 Garching, Germany.
  {\texttt{magdalena.schreter@tum.de}}}

\author[14]{Jan Philipp Thiele}
 \affil[14]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

\author[15]{Bruno~Turcksin}

\author[16]{David Wells}
\affil[16]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item changes of interface of AffineConstraints
  \item clean up: orientation
\end{itemize}
%
The changelog lists more than X other features and bugfixes.

@@

\begin{itemize}
\item VectorizedArray for ARM Neon
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interface to the \trilinos \tpetra stack}\label{sec:tpetra}

\begin{itemize}
  \item What is a \textit{stack}? [Thiele]
  \item The \epetra stack is deprecated [Thiele]
  \item Short overview capabilities of \epetra (MPI parallel, fixed types) [Thiele]
  \item Short overview capabilities of \tpetra (MPI+X via Kokkos, auto diff types, Templated petra) [Thiele]
  \item Current state of the interface (Tpertra based linear algebra, direct solver from Amesos2, preconditioners from Ifpack2) [Thiele \& Kinnewig]
  \item User relevant changes from \epetra: incompatibilities, removed options, changes in the constructor. [Thiele \& Kinnewig]
\end{itemize}

>>>>

\newcommand{\specialword}[1]{\texttt{#1}}
\newcommand{\dealii}{{\specialword{deal.II}}\xspace}
\newcommand{\pfrst}{{\specialword{p4est}}\xspace}
\newcommand{\trilinos}{{\specialword{Trilinos}}\xspace}
\newcommand{\aspect}{\specialword{Aspect}\xspace}
\newcommand{\petsc}{\specialword{PETSc}\xspace}
\newcommand{\snes}{{\specialword{SNES}}\xspace}
\newcommand{\ts}{{\specialword{TS}}\xspace}
\newcommand{\petscsf}{{\specialword{SF}}\xspace}
\newcommand{\cmake}{{\specialword{CMake}}\xspace}
\newcommand{\candi}{{\specialword{candi}}\xspace}
\newcommand{\sundials}{{\specialword{SUNDIALS}}\xspace}
\newcommand{\kinsol}{{\specialword{KINSOL}}\xspace}
\newcommand{\ida}{{\specialword{IDA}}\xspace}
\newcommand{\arkode}{{\specialword{ARKODE}}\xspace}
\newcommand{\boost}{{\specialword{Boost}}\xspace}
\newcommand{\kokkos}{{\specialword{Kokkos}}\xspace}

@@

\author[8]{Timo~Heister}
 \affil[8]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA.
   {\texttt{heister@clemson.edu}}}

\author[9]{Luca~Heltai}
\affil[9]{University of Pisa, Italy.}

 \author[10,11]{Martin~Kronbichler}
 \affil[10]{Faculty of Mathematics, Ruhr University Bochum,
   Universit\"atsstr.~150, 44780 Bochum, Germany.
 {\texttt{martin.kronbichler@rub.de}}}
 \affil[11]{Institute of Mathematics,
   University of Augsburg,
   Universit\"atsstr.~12a, 86159 Augsburg, Germany.
   }

\author[12]{Matthias~Maier}
\affil[12]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[11,13]{Peter Munch}
 \affil[13]{Uppsala University, Sweden.
  {\texttt{peter.munch@it.uu.se}}}

\author[14]{Magdalena Schreter-Fleischhacker}
 \affil[14]{Institute for Computational Mechanics, Technical University of Munich, Boltzmannstraße 15, 85748 Garching, Germany.
  {\texttt{magdalena.schreter@tum.de}}}

\author[15]{Jan Philipp Thiele}
 \affil[15]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

\author[16]{Bruno~Turcksin}

\author[17]{David Wells}
\affil[17]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
\item changes of interface of AffineConstraints
\item clean up: orientation
\item various performance improvements throughout the library
\item the \texttt{SolverGMRES} class now offers a third orthogonalization
  method, the classical Gram--Schmidt method with delayed orthogonalization
  \cite{Bielich2022}. Furthermore, the solver now specifies the maximal basis
  size of the Arnoldi basis, rather than the number of auxiliary vectors.
\end{itemize}
%
The changelog lists more than X other features and bugfixes.

@@

\begin{itemize}
\item VectorizedArray for ARM Neon
\item Improvement for evaluation of values and gradients for
  $H$(div)-conforming Raviart--Thomas elements on non-Cartesian elements
\item Improved internal data structures of the tensor-product evaluators as
  well as the evaluators for simplex elements, which speed up the evaluation
  in several scenarios, especially multi-component systems.
\end{itemize}

@@
